Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-08-06 manuscript.Rmd
fix titles

title: "A tutorial on how to do the same thing more than once"

@@

## Dynamic document generation

@@

@@

Another challenge is that PAC requires more programming expertise than a usual analysis.
In contrast to a reproducible script, which should work on the same data, a PAC must work on different data of similar structure.
We call the property of code that can run on different inputs from a similar context and produce valid outputs "reusability".
This property is based on reproducibility but requires the researcher to more carefully write the software [@lanerganSoftwareEngineeringReusable1989] such that it is _build-for-reuse_ [@al-badareenReusableSoftwareComponents2010].
The reproducible workflow we present here is heavily automated and hence promotes reusability.
Furthermore, adhering to principles of reusability typically removes errors in the code and thus increases the likelihood that the statistical analysis is correct

>>>>

title: "Reproducible Research in R: A tutorial on how to do the same thing more than once"

@@

## Using dynamic document generation

@@

## Manage software and file dependencies

@@
